Wu-Tang Clan

### 2015-03-03 rmtw/a5/latex8.tex
Wu-Tang Clan
sda
Data synthesis

\title{Assignment 5}

@@

\subsubsection{Review Protocol}
The next step was to (<- XXX re-phrase that) define the review protocol. The list of databases included can be seen in Table I. The included databases have been chosen based on recommendations in \cite{brereton2007lessons}. SpringerLink was included as advised in \cite{kitchenham2007guidelines}. The databases were divided evenly between the two researchers.

@@

The inclusion criteria were defined as follows: \newline
\begin{itemize} 
\item Studies including examples about the application of MDSD in industry
\end{itemize}

The exclusion criteria were defined as follows: \newline
\begin{itemize}
\item Informal papers (no defined research questions, no methodology)
\item Non-peer reviewed papers (books, white papers etc.)
\end{itemize}

@@

@@

@@

@@

Data from ongoing studies will be not included in our data extraction. The primary reason behind this stance is that we are interested in the complete adoption of MDSD and as such a study which is either examining the adoption and is half way through will not help us answer this question.

@@

We will probably want to qualitative. We're not really going after data points as such. Perhaps even a narrative.

If we do, we'll need a sensitivity analysis to

>>>>

\title{Wu-Tang Clan}

@@

\subsubsection{Review Protocol}
Subsequently, the reivew protocol was defined. The list of databases included can be seen in Table I. The included databases have been chosen based on recommendations in \cite{brereton2007lessons}. SpringerLink was included as advised in \cite{kitchenham2007guidelines}. The databases were divided evenly between the two researchers.

@@

The inclusion criteria were defined as follows: \newline
\begin{itemize} 
\item Studies including examples about the application of MDSD in industry
\item Studies carried out using a qualitative methodology
\end{itemize}

The exclusion criteria were defined as follows: \newline
\begin{itemize}
\item Informal papers (no defined research questions, no methodology)
\item Non-peer reviewed papers (books, white papers etc.)
\item Studies carried out using a quantitative methodology
\end{itemize}

@@

\subsubsection{Study Selection}

@@

\subsubsection{Quality Assessment}

@@

\subsubsection{Data Extraction}

@@

Data from ongoing studies was not included in our data extraction. The primary reason behind this stance is that we were interested in the complete adoption of MDSD and as such a study which is either examining the adoption and is half way through will not help us answer this question.

@@

\subsubsection{Data Synthesis}

As our study included only qualitative studies, a reciprocal translation was was performed. As we focused upon qualitative studies, we were faced with comparing studies consisting of mostly natural language. Consequently, there were some studies which contained differing language for similar concepts but the use of a reciprocal study allowed us to translate the studies so that they could be compared to each other.
